A Software Engineering Perspective on \\ OpenMP and PThreads

### 2017-10-16 sections/07-conclusion.tex
Added paragraph discussing some threats to validity aspects

Contrary to our analysis, students reported the perception that using
\textit{OpenMP} made it easier to improve the performance of the sequential
code we provided.  Our analysis of their submissions revealed that the majority
of the students ($52.2\%$) achieved better performance in the assignment with
either \textit{OpenMP} ($17.4\%$) or \textit{Pthreads} ($34.8\%$).
Contradicting the perception of the students, the implementation using
\textit{Pthreads} achieved better performance in twice the submissions.

@@

>>>>

Contrary to our analysis, students reported the perception that using
\textit{OpenMP} made it easier to improve the performance of the sequential
code we provided.  Our analysis of their submissions revealed that most 
of the students ($52.2\%$) achieved better performance in the assignment with
either \textit{OpenMP} ($17.4\%$) or \textit{Pthreads} ($34.8\%$).
Contradicting the perception of the students, the implementation using
\textit{Pthreads} achieved better performance in twice the submissions.

@@

In our study we have not compared the material used for teaching both
technologies in depth. In particular, we have not made any comparison regarding
the difficulty associated with the notes used for teaching both technologies.
Thus, on the matter of threats to the study validity, the students' perceptions
of the difficulty level of the references, used during the class, were not
taken into account. Also, in order to provide a more in-depth statistical
analysis, the study needs to be performed in several classes of the Concurrent,
Parallel and Distributed Computing courses.  Nevertheless, this pilot study
presents some great insights that will help devise statistical hypothesis that
should be tested in later studies.
